Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach

### 2014-06-06 manuscripts/manuscript.Rmd
fix missing )

setA = as.numeric(c(r = p1[1], K = p2[1], theta = p3[1]))
setB = as.numeric(c(r = p1[2], K = p2[2], theta = p3[2])
setC = as.numeric(c(r = p1[3], K = p2[3], C = p3[3]))
setD = as.numeric(c(r = p1[4], K = p2[4], C = p3[4]))
AllenParameterSets <- rbind(setA, setB)
MyersParameterSets <- rbind(setC,setD)

>>>>

setA = as.numeric(c(r = p1[1], K = p2[1], theta = p3[1]))
setB = as.numeric(c(r = p1[2], K = p2[2], theta = p3[2]))
setC = as.numeric(c(r = p1[3], K = p2[3], C = p3[3]))
setD = as.numeric(c(r = p1[4], K = p2[4], C = p3[4]))
AllenParameterSets <- rbind(setA, setB)
MyersParameterSets <- rbind(setC,setD)
